### 2009-08-14 papers/SBMF2009/Presentation/content/1_introduction.tex

\begin{itemize}[<+->]
  \item The B method supports the construction of safety systems
  \begin{itemize}
    \item Until the implementation model
    \item But part of this translation is not guaranteed by formal means\\
    \begin{center}
       \includegraphics[height=.5\textheight]{figures/b-method-actual_new.pdf}
    \end{center}
       \begin{itemize} \item   \small{The transformation process can introduce small bugs}
       \end{itemize}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}[<+->]
    \item We proposed [Dantas, 2008]  a approach to extend the formal verification
    \item One key of this approach is the formal model of the instruction set  of execution platform % of such assembly languages
      \\ \begin{center} \includegraphics[height=.5\textheight]{figures/b-method-ideal_new.pdf} \end{center}

\end{itemize}
% TO-DO Ajustar a figura

@@

\begin{itemize}[<+->]
  \item We developed libraries of hardware models%.The modelling is builded using some  developed libraries
  \item The libraries have common concepts that can be used to others platforms of 8 or 16 bits
  \item Utilities of this formal model:
  \begin{itemize}
    \item Documentation
    \item Simulation
    \item The formal verification until the assembly level
    \item A possible support to verify the Z80 design

>>>>

\begin{itemize}[<+->]
  \item The B method supports the construction of safety systems
  \begin{itemize}
    \item From design model
    \item To implementation model
    \item But part of this translation is not guaranteed by formal means\\
    \begin{center}
       \includegraphics[height=.5\textheight]{figures/b-method-actual_new.pdf}
    \end{center}
       \begin{itemize} \item   \small{The transformation process can introduce small bugs}
       \end{itemize}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}%[<+->]
    \item We proposed a approach [Dantas, 2008] to extend the formal
    verification
    \item One key element of this approach is the formal model of the
    instruction set of execution platform % of such assembly languages
     \\ \begin{center}     \includegraphics[height=.5\textheight]{figures/b-method-ideal_new.pdf} \end{center}
\end{itemize}
	\note{...................}
\end{frame}

@@

\begin{itemize}[<+->]
  \item We developed libraries of hardware models%.The modelling is builded using some  developed libraries
  \item The libraries have common concepts that can be used to others platforms of 8 or 16 bits
  \item Utilities of this formal model:
  \begin{itemize}
    \item Documentation
    \item Simulation
    \item The formal verification until the assembly level
    \item A possible support to verify the Z80 design
    	\item Reference for verification of Z80 hardware implementations

### 2009-08-14 papers/SBMF2009/Presentation/content/7_Conclusions.tex
version almost conclused

 \begin{frame}
 \frametitle{Considerations about the work}

 \begin{itemize}
   \item It can be used to: \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 
    \includegraphics[width=.2\textwidth]{figures/processador_generico.jpg}
 	\begin{itemize} 
 	  \item Identify  errors on the official reference
 	  \item Important to  assembly programmers
 	  \item Formal verification until assembly language \\
 	   \includegraphics[height=.25\textheight]{figures/dutos.png} \ \ \ \ \ \ \ \ \ \ 
        \includegraphics[height=.25\textheight]{figures/trem_bala2.png} 
 	\end{itemize} 
 \end{itemize}

@@

\begin{frame}
  \frametitle{Sugestions/Doubts/Critics }
  	\begin{center}
    {\huge ?}\\
    \includegraphics[width=.5\textwidth]{figures/rodin.png}\\
    \large{ If you prefer, you can send an e-mail to 
    %\textcolor{blue!70!black}{\textit{valerio}}@ppgsc.ufrn.br or
    \textcolor{blue!70!black}{\textit{valerio.jr}}@gmail.com 
    }
	\end{center}

>>>>

 \begin{frame}
 \frametitle{Conclusions about the Work}

 \begin{itemize}
   \item Contributions: \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \
    \includegraphics[width=.2\textwidth]{figures/processador_generico.jpg}
 	\begin{itemize} 
 	  \item Identify  errors in the official reference
 	  \item Help assembly programmers
 	  \item Formal verification until assembly language 
     \end{itemize} 
     \item Future work is the verified development of a petroleum production test system\\ 
     \begin{center}   
 	   \includegraphics[height=.25\textheight]{figures/dutos.png}
	 \end{center}%\ \ \ \ \ \ \ \ \ \ 
     %   \includegraphics[height=.25\textheight]{figures/trem_bala2.png}

 \end{itemize}

@@

\begin{frame}
  \frametitle{Sugestions/Doubts/Critics }
  	\begin{center}
    {\huge ?}\\
    \includegraphics[width=.5\textwidth]{figures/rodin.png}\\
    \large{ If you prefer, you can send an e-mail to 
    %\textcolor{blue!70!black}{\textit{valerio}}@ppgsc.ufrn.br or
    \textcolor{blue!70!black}{\textit{valerio.jr}}@gmail.com \\
    Project available at http://code.google.com/p/b2asm
    }
	\end{center}
